Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalnew\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-06-17 ms.tex
fixing numbers

\newcommand{\Nfp}{7}
\newcommand{\Nvalidated}{20}
\newcommand{\Nlimbo}{9} %adds up to 36
\newcommand{\Nvalnew}{16} % 4 previously validated

@@

\title{Stellar and Planetary Properties of \KT\ Campaign 1
Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving
Earth-like Insolation}

@@

Four of the presented candidates have FPP $>$90\%;
these are considered to be likely false positives.
On the other hand, 23 candidates
have FPP $<$ 1\%.
Two of these are found to be caused by systematics
in the transit search noise model (details in \S\ref{sec:systematics}), and
so we identify those as false positives.
Four more of these 23 might plausibly be caused by
contamination by detected stellar companions within the photometric apertures
(see \S\ref{sec:background}), so we keep these as candidates.

This leaves 19 candidates that we statistically validate as planets, plus one
additional planets that \texttt{vespa} does not validate but have been previously
identified in the literature \citep{Crossfield15, Armstrong15b}.
So in total, of the 36 candidates, 20 are secure planets,
16 of which we here validate for the first time.

@@

We have presented stellar parameters for all planet candidates systems identified by
\paperit.
We statistically validate \Nvalidated\ of the 36 candidates as bona fide planets, and we
identify \Nfp\ as false positives.
Of these planets, 4 have been previously validated in other works, while 14 are
validated here for the first time.
The systems not validated as planets or false positives remain as planet candidates.

@@

As stated in \textsection\ref{sec:stellarparams}, we infer stellar parameters using the
Dartmouth models, with a mass upper limit of $3.7 M_\odot$.
Given the location of the \Ci\ field with respect to the galactic plane, we expect a low
contamination rate by halo giants.
However, there are a few stars that are possibly miscategorized giants.
EPIC 201257461 is identified in the RAdial Velocity Experiment (RAVE) Fourth Data Release
as a target with $\logg = 3.18$, consistent with that of a giant star.
It is therefore perhaps not surprising that this system is flagged as a false positive based on
the transit shape.
EPIC 201929294, with a proper motion of $0.010\arcsec$ yr$^{-1}$ \citep{Zacharias12}  has
a reduced proper motion consistent with that of a giant star.
While suggestive, this observation does not definitively provide information about the
nature of this target.
Likewise, our false positive analysis is neither able to confirm nor exclude the planetary
nature of the observed transit signal around this target.

>>>>

\newcommand{\Nfp}{7}
\newcommand{\Nvalidated}{19}
\newcommand{\Nlimbo}{9} %adds up to 36
\newcommand{\Nvalnew}{16} % 4 previously validated

@@

\title{Stellar and Planetary Properties of \KT\ Campaign 1
Candidates and Validation of \Nvalnew\ Systems, Including a Planet Receiving
Earth-like Insolation}

@@

Four of the presented candidates have FPP $>$90\%;
these are considered to be likely false positives.
On the other hand, 24 candidates
have FPP $<$ 1\%.
Two systems, one of which is a planet candidate by the above definition,
 are found to be caused by systematics
in the transit search noise model (details in \S\ref{sec:systematics}), and
so we identify those as false positives.
Four of the transit signals might plausibly be caused by
contamination by detected stellar companions within the photometric apertures
(see \S\ref{sec:background}), so we keep these as candidates.

This leaves 19 candidates that we statistically validate as planets, plus one
additional planet that \texttt{vespa} does not validate but has been previously
identified in the literature \citep{Crossfield15, Armstrong15b}.
So in total, of the 36 candidates, 20 are secure planets,
16 of which we validate here for the first time.

@@

We have presented stellar parameters for all planet candidates systems identified by
\paperit.
We statistically validate \Nvalidated\ of the 36 candidates as bona fide planets, and we
identify \Nfp\ as false positives.
Of these planets, 3 have been previously validated in other works, while \Nvalnew\ are
validated here for the first time.
The systems not validated as planets or false positives remain as planet candidates.

@@
